systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-11-22 paper/trunk/systemfit_estimation.tex
the unifying properties of the estimators are (almost fully) exploited now in subsection "Estimation" (requested by reviewer 2); splitted subsection "Estimation" into "Estimation with only exogenous regressors" (OLS, WLS, SUR) and "Estimation with endogenous regressors" (2SLS, W2SLS, 3SLS); adjusted references to sections and equations in the modified subsections(s)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@832 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation}\label{sec:Estimation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The Ordinary Least Squares (OLS) estimator of the system 
is obtained by
\begin{equation}
   \bHat_{OLS} = \left( X'X \right)^{-1} X'y .
   \label{eq:ols}
\end{equation}
These estimates are efficient only if the disturbance terms are not
contemporaneously correlated, which means
$\sigma_{ij} = 0 \; \forall \; i \neq j$.
If the whole system is treated as one single equation,
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{OLS} \right] = \sHat^2 \left( X'X \right)^{-1} ,
   \label{eq:olsCovSameSigma}
\end{equation}
where $\sHat^2$ is the estimated variance of the disturbances.
This assumes that the disturbances of all equations have the
same variance $(\E [ u_{it}^2 ] = \sigma^2 \, \forall \, i)$.

If the disturbance terms of the individual equations
are allowed to have different variances,
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{OLS} \right] = \left( X' \OHat^{-1} X \right)^{-1} ,
   \label{eq:olsCovSingleSigma}
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

If no cross-equation parameter restrictions are imposed, the simultaneous 
OLS estimation of the system leads to the same parameter estimates 
as an equation-wise OLS estimation.
The covariance matrix of the parameters from an equation-wise
OLS estimation is equal to the covariance matrix obtained
by equation (\ref{eq:olsCovSingleSigma}).

@@

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j$,
where $\sigma_i^2 = \E [ u_{it}^2 ])$.
The WLS estimator can be obtained by
\begin{equation}
   \bHat_{WLS} = \left( X' \OHat^{-1} X \right)^{-1} X' \OHat^{-1} y ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the variance
of the (estimated) residuals in the $i$th equation.
Theoretically, $\sHat_{ii}$ should be the variance of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

These estimates are (asymptotically) efficient
if the disturbance terms are not contemporaneously correlated.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{WLS} \right] = \left( X' \OHat^{-1} X \right)^{-1} .
\end{equation}
If no cross-equation parameter restrictions are imposed,
the parameter estimates are equal to the OLS estimates.

@@

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
However, the true covariance matrix of the disturbance terms
is generally unknown.
The textbook solution for this problem is
a Feasible Generalized Least Squares (FGLS) estimation.
As the FGLS estimator is based on
an estimated covariance matrix of the disturbance terms,
it is only asymptotically efficient.
It should be noted that while an unbiased OLS or WLS estimation requires only that
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i ' X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( \E \left[ u_i ' X_j \right] = 0 \; \forall \; i, j )$.

The SUR estimator can be obtained by
\begin{equation}
   \bHat_{SUR} = \left( X' \OHat^{-1} X \right)^{-1} X' \OHat^{-1} y ,
   \label{eq:sur}
\end{equation}
where $\OHat = \SHat \otimes I$ and
$\SHat$ is the estimated covariance matrix of the disturbance terms.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{SUR} \right] = \left( X' \OHat^{-1} X \right)^{-1} .
   \label{eq:surCov}
\end{equation}

@@

If the regressors of one or more equations are correlated 
with the disturbances ($\E \left[ u_i' X_i \right] \neq 0$),
OLS estimates are biased.
This can be circumvented by an instrumental variable (IV)
two-stage least squares (2SLS) estimation.
The instrumental variables for each equation $H_i$ 
can be either different or identical for all equations.
They must not be correlated with
the disturbance terms of the corresponding equation 
($\E \left[ u_i' H_i \right] = 0$).

At the first stage new ('fitted') regressors are obtained by
\begin{equation}
   \XHat_i = H_i \left( H_i' H_i \right)^{-1} H_i' X .
\end{equation}
At the second stage, the unbiased two-stage least squares estimates
of $\beta$ are obtained by
\begin{equation}
   \bHat_{2SLS} = \left( \XHat' \XHat \right)^{-1}
   \XHat' y .
   \label{eq:beta2sls}
\end{equation}
If the whole system is treated as one single equation,
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{2SLS} \right] = \sHat^2 \left( \XHat'
   \XHat \right)^{-1} ,
   \label{eq:2slsCovSameSigma}
\end{equation}
where $\sHat^2$ is the estimated variance of the disturbance terms.
If the disturbance terms of the individual equations
are allowed to have different variances, 
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{2SLS} \right] = \left( \XHat' \OHat^{-1}
   \XHat \right)^{-1} ,
   \label{eq:2slsCovSingleSigma}
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

@@

The Weighted Two-Stage Least Squares (W2SLS) estimator of the system 
is obtained by
\begin{equation}
   \bHat_{W2SLS} = \left( \XHat' \OHat^{-1} \XHat
   \right)^{-1} \XHat' \OHat^{-1} y ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{W2SLS} \right] = \left( \XHat' \OHat^{-1}
   \XHat \right)^{-1} .
\end{equation}

@@

If the regressors are correlated with the disturbances 
($\E \left[ u_i' X_i \right] \neq 0$) and
the disturbances are contemporaneously correlated, 
a Feasible Generalized Least Squares (FGLS) version of the two-stage least squares
estimation leads to consistent and asymptotically more efficient estimates.
This estimation procedure is generally called °Three-stage Least
Squares° (3SLS) \citep{zellner62b}.

The standard 3SLS estimator can be obtained by
\begin{equation}
   \bHat_{3SLS} = \left( \XHat' \OHat^{-1} \XHat
   \right)^{-1} \XHat' \OHat^{-1} y ,
   \label{eq:3slsGls}
\end{equation}
where $\OHat = \SHat \otimes I$ and
$\SHat$ is the estimated covariance matrix of the disturbance terms.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{3SLS} \right] = \left( \XHat' \OHat^{-1}
   \XHat \right)^{-1} .
   \label{eq:cov3sls}
\end{equation}
While an unbiased 2SLS or W2SLS estimation requires only that
the instrumental variables and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i' H_i \right]) = 0 \; \forall \; i )$,
\cite{schmidt90} points out that this estimator is only consistent 
if all disturbance terms and all instrumental variables are uncorrelated
$( \E \left[ u_i' H_j \right]) = 0 \; \forall \; i, j )$.

Since there might be occasions where this cannot be avoided,
\cite{schmidt90} analyses other approaches to obtain 3SLS estimators.
One of these approaches based on instrumental variable estimation
(3SLS-IV) is
\begin{equation}
   \bHat_{3SLS-IV} = \left( \XHat' \OHat^{-1} X
   \right)^{-1} \XHat' \OHat^{-1} y .
   \label{eq:3slsIv}
\end{equation}
An estimator of the covariance matrix of the estimated 3SLS-IV parameters is
\begin{equation}
   \COVHat \left[ \bHat_{3SLS-IV} \right] = \left( \XHat' \OHat^{-1}
   X \right)^{-1} .
\end{equation}
Another approach based on the Generalized Method of Moments (GMM)
estimator (3SLS-GMM) is
\begin{equation}
   \bHat_{3SLS-GMM} = \left( X' H \left( H' \OHat H \right)^{-1}
   H' X \right)^{-1} X' H \left( H' \OHat H \right)^{-1} H' y
   \label{eq:3slsGmm}
\end{equation}
with
\begin{equation}
   H =
   \left[ \begin{array}{cccc}
      H_1 & 0 & \cdots & 0\\
      0 & H_2 & \cdots & 0\\
      \vdots & \vdots & \ddots & \vdots\\
      0 & 0 & \cdots & H_G
   \end{array}\right] .
\end{equation}
An estimator of the covariance matrix of the estimated 3SLS-GMM parameters is
\begin{equation}
   \COVHat \left[ \bHat_{3SLS-GMM} \right] =
   \left( X' H \left( H' \OHat H \right)^{-1} H' X \right)^{-1} .
\end{equation}
A fourth approach developed by \cite{schmidt90} himself is
\begin{equation}
   \bHat_{3SLS-Schmidt} = \left( \XHat' \OHat^{-1} \XHat
   \right)^{-1} \XHat' \OHat^{-1}
   H \left( H' H \right)^{-1} H' y .
   \label{eq:3slsSchmidt}
\end{equation}
An estimator of the covariance matrix of these estimated parameters is
\begin{align}
   \COVHat \left[ \bHat_{3SLS-Schmidt} \right] = &
   \left( \XHat' \OHat^{-1}  \XHat \right)^{-1}
   \XHat' \OHat^{-1} H \left( H' H \right)^{-1} H' \OHat H \\
   & \left( H' H \right)^{-1} H' \OHat^{-1} \XHat
   \left( \XHat' \OHat^{-1}  \XHat \right)^{-1} .
   \nonumber
\end{align}
The econometrics software \proglang{EViews} uses
\begin{equation}
   \bHat_{3SLS-EViews} = \bHat_{2SLS} +
   \left( \XHat' \OHat^{-1} \XHat \right)^{-1}
   \XHat' \OHat^{-1} \left( y - X \bHat_{2SLS} \right) ,
   \label{eq:3slsEViews}
\end{equation}
where $\bHat_{2SLS}$ is the two-stage least squares estimator
as defined by (\ref{eq:beta2sls}).
\proglang{EViews} uses the standard 3SLS formula (\ref{eq:cov3sls}) to
calculate an estimator of the covariance matrix of the estimated parameters.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation with only exogenous regressors}
\label{sec:Estimation-ols-wls-sur}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If all regressors are exogenous,
the system of equations~(\ref{eq:model})
can be consistently estimated by Ordinary Least Squares (OLS),
Weighted Least Squares (WLS), and Seemingly Unrelated Regression (SUR).
These estimators can be obtained by
\begin{equation}
   \bHat = \left( X' \OHat^{-1} X \right)^{-1} X' \OHat^{-1} y .
   \label{eq:ols-wls-sur}
\end{equation}
The covariance matrix of these estimators
can be estimated by
\begin{equation}
   \COVHat \left[ \bHat \right] = \left( X' \OHat^{-1} X \right)^{-1} .
   \label{eq:cov-ols-wls-sur}
\end{equation}

@@

The Ordinary Least Squares (OLS) estimator is based on the assumption
that the disturbance terms are not contemporaneously correlated
$(\sigma_{ij} = 0 \; \forall \; i \neq j)$
and have the same variance in each equation
$( \sigma_i^2 = \sigma_j^2 \, \forall \, i, j$,
where $\sigma_i^2 = \E [ u_{it}^2 ])$.
In this case, $\OHat$ in equation~(\ref{eq:ols-wls-sur})
is equal to $I_{G \cdot T}$ and thus, cancels out.
The OLS estimator is efficient,
as long as the disturbances are not contemporaneously correlated.

If the whole system is treated as one single equation,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\sHat^2 I_{G \cdot T}$,
where $\sHat^2$ is the estimated variance of the disturbances.
This assumes that the disturbances of all equations have the
same variance $(\E [ u_{it}^2 ] = \sigma^2 \, \forall \, i)$.
If the disturbance terms of the individual equations
are allowed to have different variances,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

If no cross-equation parameter restrictions are imposed, the simultaneous 
OLS estimation of the system leads to the same parameter estimates 
as an equation-wise OLS estimation.
The covariance matrix of the parameters from an equation-wise
OLS estimation is equal to the covariance matrix obtained
by equation~(\ref{eq:cov-ols-wls-sur})
with $\OHat$ equal to $\SHat \otimes I_T$.

@@

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j)$.
In this case, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance terms in the $i$th equation.
Theoretically, $\sHat_{ii}$ should be the variance of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

The WLS estimator is (asymptotically) efficient only
if the disturbance terms are not contemporaneously correlated.
If no cross-equation parameter restrictions are imposed,
the parameter estimates are equal to OLS estimates.

@@

If the disturbances are contemporaneously correlated, a Generalized
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
However, the true covariance matrix of the disturbance terms
is generally unknown.
The textbook solution for this problem is
a Feasible Generalized Least Squares (FGLS) estimation.
As the FGLS estimator is based on
an estimated covariance matrix of the disturbance terms,
it is only asymptotically efficient.
In case of an SUR estimator, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\SHat$ is the estimated covariance matrix of the disturbance terms.

It should be noted that while an unbiased OLS or WLS estimation requires only that
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i ' X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( \E \left[ u_i ' X_j \right] = 0 \; \forall \; i, j )$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimation with endogenous regressors}
\label{sec:Estimation-2sls-w2sls-3sls}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If the regressors of one or more equations are correlated
with the disturbances ($\E \left[ u_i' X_i \right] \neq 0$),
OLS, WLS, and SUR estimates are biased.
This can be circumvented by a
two-stage least squares (2SLS),
weighted two-stage least squares (W2SLS),
or a three-stage least squares (3SLS) estimation
with instrumental variables (IV).
The instrumental variables for each equation $H_i$ 
can be either different or identical for all equations.
They must not be correlated with
the disturbance terms of the corresponding equation 
($\E \left[ u_i' H_i \right] = 0$).

At the first stage new ('fitted') regressors are obtained by
\begin{equation}
   \XHat_i = H_i \left( H_i' H_i \right)^{-1} H_i' X .
\end{equation}
Then, these 'fitted' regressors are used
to obtain unbiased 2SLS, W2SLS, or 3SLS estimates of $\beta$ by
\begin{equation}
   \bHat
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} \XHat' \OHat^{-1} y .
   \label{eq:2sls-w2sls-3sls}
\end{equation}
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat \right]
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} .
   \label{eq:cov-2sls-w2sls-3sls}
\end{equation}

@@

The Two-Stage Least Squares (2SLS) estimator
is based on the same assumptions as the OLS estimator.
Accordingly, $\OHat$ in equation~(\ref{eq:2sls-w2sls-3sls})
is equal to $I_{G \cdot T}$ and thus, cancels out.
Like for the OLS estimator,
the whole system can be treated either as one single equation
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\sHat^2 I_{G \cdot T}$,
or the disturbance terms of the individual equations
are allowed to have different variances
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$.

@@

The Weighted Two-Stage Least Squares (W2SLS) estimator allows
for different variances of the disturbance terms in the different equations.
Hence, $\OHat$ in equations~(\ref{eq:2sls-w2sls-3sls})
and~(\ref{eq:cov-2sls-w2sls-3sls})
is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$.
If no cross-equation parameter restrictions are imposed,
the parameter estimates are equal to the 2SLS estimates.

@@

If the disturbances are contemporaneously correlated,
a Feasible Generalized Least Squares (FGLS) version of the two-stage least squares
estimation leads to consistent and asymptotically more efficient estimates.
This estimation procedure is generally called °Three-stage Least
Squares° (3SLS) \citep{zellner62b}.
The standard 3SLS estimator and its covariance matrix are obtained by
equations~(\ref{eq:2sls-w2sls-3sls}) and~(\ref{eq:cov-2sls-w2sls-3sls})
with $\OHat$ equal to $\SHat \otimes I_T$,
where $\SHat$ is the estimated covariance matrix of the disturbance terms.

While an unbiased 2SLS or W2SLS estimation requires only that
the instrumental variables and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i' H_i \right]) = 0 \; \forall \; i )$,
\cite{schmidt90} points out that this estimator is only consistent 
if all disturbance terms and all instrumental variables are uncorrelated
$( \E \left[ u_i' H_j \right]) = 0 \; \forall \; i, j )$.

Since there might be occasions where this cannot be avoided,
\cite{schmidt90} analyses other approaches to obtain 3SLS estimators.
One of these approaches based on instrumental variable estimation
(3SLS-IV) is
\begin{equation}
   \bHat_{3SLS-IV} = \left( \XHat' \OHat^{-1} X
   \right)^{-1} \XHat' \OHat^{-1} y .
   \label{eq:3slsIv}
\end{equation}
An estimator of the covariance matrix of the estimated 3SLS-IV parameters is
\begin{equation}
   \COVHat \left[ \bHat_{3SLS-IV} \right] = \left( \XHat' \OHat^{-1}
   X \right)^{-1} .
\end{equation}
Another approach based on the Generalized Method of Moments (GMM)
estimator (3SLS-GMM) is
\begin{equation}
   \bHat_{3SLS-GMM} = \left( X' H \left( H' \OHat H \right)^{-1}
   H' X \right)^{-1} X' H \left( H' \OHat H \right)^{-1} H' y
   \label{eq:3slsGmm}
\end{equation}
with
\begin{equation}
   H =
   \left[ \begin{array}{cccc}
      H_1 & 0 & \cdots & 0\\
      0 & H_2 & \cdots & 0\\
      \vdots & \vdots & \ddots & \vdots\\
      0 & 0 & \cdots & H_G
   \end{array}\right] .
\end{equation}
An estimator of the covariance matrix of the estimated 3SLS-GMM parameters is
\begin{equation}
   \COVHat \left[ \bHat_{3SLS-GMM} \right] =
   \left( X' H \left( H' \OHat H \right)^{-1} H' X \right)^{-1} .
\end{equation}
A fourth approach developed by \cite{schmidt90} himself is
\begin{equation}
   \bHat_{3SLS-Schmidt} = \left( \XHat' \OHat^{-1} \XHat
   \right)^{-1} \XHat' \OHat^{-1}
   H \left( H' H \right)^{-1} H' y .
   \label{eq:3slsSchmidt}
\end{equation}
An estimator of the covariance matrix of these estimated parameters is
\begin{align}
   \COVHat \left[ \bHat_{3SLS-Schmidt} \right] = &
   \left( \XHat' \OHat^{-1}  \XHat \right)^{-1}
   \XHat' \OHat^{-1} H \left( H' H \right)^{-1} H' \OHat H \\
   & \left( H' H \right)^{-1} H' \OHat^{-1} \XHat
   \left( \XHat' \OHat^{-1}  \XHat \right)^{-1} .
   \nonumber
\end{align}
The econometrics software \proglang{EViews} uses
\begin{equation}
   \bHat_{3SLS-EViews} = \bHat_{2SLS} +
   \left( \XHat' \OHat^{-1} \XHat \right)^{-1}
   \XHat' \OHat^{-1} \left( y - X \bHat_{2SLS} \right) ,
   \label{eq:3slsEViews}
\end{equation}
where $\bHat_{2SLS}$ is the two-stage least squares estimator
as defined above.
\proglang{EViews} uses the standard 3SLS formula~(\ref{eq:cov-2sls-w2sls-3sls}) to
calculate an estimator of the covariance matrix of the estimated parameters.

### 2007-11-22 paper/trunk/systemfit_other.tex
the unifying properties of the estimators are (almost fully) exploited now in subsection "Estimation" (requested by reviewer 2); splitted subsection "Estimation" into "Estimation with only exogenous regressors" (OLS, WLS, SUR) and "Estimation with endogenous regressors" (2SLS, W2SLS, 3SLS); adjusted references to sections and equations in the modified subsections(s)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@832 591db2bd-e0a0-4d22-8c19-2192dbb7da31

If a system of equations is estimated by an unrestricted OLS and
the covariance matrix of the parameters is calculated
by~(\ref{eq:olsCovSingleSigma}),
the estimated parameters and their standard errors are identical
to an equation-wise OLS estimation.
In this case, it is reasonable to use the degrees of freedom of
each single equation,
because this yields the same $p$ values as the equation-wise
OLS estimation.

In contrast, if a system of equations is estimated with many
cross-equation restrictions and
the covariance matrix of an OLS estimation is calculated
by~(\ref{eq:olsCovSameSigma}),
the system estimation is similar to a single equation estimation.
Therefore, in this case, it seems to be reasonable to use the degrees
of freedom of the entire system.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is
\begin{equation}
  m = \left( \bHat_{2SLS} - \bHat_{3SLS} \right)^{'}
      \left( \COVHat \left[ \bHat_{2SLS} \right] -
             \COVHat \left[ \bHat_{3SLS} \right] \right)
      \left( \bHat_{2SLS} - \bHat_{3SLS} \right) ,
\label{eq:hausman}
\end{equation}
where $\bHat_{2SLS}$ and $\COVHat \left[ \bHat_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\bHat_{3SLS}$ and $\COVHat \left[ \bHat_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypothesis this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

>>>>

If a system of equations is estimated by an unrestricted OLS and
the covariance matrix of the parameters is calculated
with $\OHat$ in equation~(\ref{eq:cov-ols-wls-sur})
equal to $\SHat \otimes I_T$,
the estimated parameters and their standard errors are identical
to an equation-wise OLS estimation.
In this case, it is reasonable to use the degrees of freedom of
each single equation,
because this yields the same $P$ values as the equation-wise
OLS estimation.

In contrast, if a system of equations is estimated with many
cross-equation restrictions and
the covariance matrix of an OLS estimation is calculated
with $\OHat$ in equation~(\ref{eq:cov-ols-wls-sur})
equal to $\sHat^2 I_{G \cdot T}$,
the system estimation is similar to a single equation estimation.
Therefore, in this case, it seems to be reasonable to use the degrees
of freedom of the entire system.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is
that the instrumental variables of each equation are
uncorrelated with the disturbance terms of all other equations
($\E \left[ u_i' H_j \right] = 0 \, \forall \, i \neq j$).
Under this null hypothesis, both the 2SLS and the 3SLS estimator are consistent,
but the 3SLS estimator is (asymptotically) more efficient.
Under the alternative hypothesis, the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent,
i.e.\ the instrumental variables of each equation are
uncorrelated with the disturbances of the same equation
($\E \left[ u_i' H_i \right] = 0 \, \forall \, i$),
but the instrumental variables of at least one equation
are correlated with the disturbances of another equation
($\E \left[ u_i' H_j \right] \neq 0 \, \exists \, i \neq j$).
The Hausman test statistic is
\begin{equation}
  m = \left( \bHat_{2SLS} - \bHat_{3SLS} \right)^{'}
      \left( \COVHat \left[ \bHat_{2SLS} \right] -
             \COVHat \left[ \bHat_{3SLS} \right] \right)
      \left( \bHat_{2SLS} - \bHat_{3SLS} \right) ,
\label{eq:hausman}
\end{equation}
where $\bHat_{2SLS}$ and $\COVHat \left[ \bHat_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from a 2SLS estimation, and
$\bHat_{3SLS}$ and $\COVHat \left[ \bHat_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from a 3SLS estimation.
Under the null hypothesis, this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

### 2007-11-22 paper/trunk/systemfit_restrictions.tex
the unifying properties of the estimators are (almost fully) exploited now in subsection "Estimation" (requested by reviewer 2); splitted subsection "Estimation" into "Estimation with only exogenous regressors" (OLS, WLS, SUR) and "Estimation with endogenous regressors" (2SLS, W2SLS, 3SLS); adjusted references to sections and equations in the modified subsections(s)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@832 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The first method is less flexible than the second%
\footnote{
While restrictions like $\beta_1 = 2 \beta_2$ can be imposed by
both methods,
restrictions like $\beta_1 + \beta_2 = 4$ can be imposed only
by the second method.
}, 
and is preferable if equality constraints for coefficients
across many equations of the system are imposed. 
Of course, these restrictions can be also imposed using
the latter method.
However, while the latter method increases the dimension of the 
matrices to be inverted during estimation, the first reduces it. 
Thus, in some cases the latter way leads to estimation problems
(e.g.\ (near) singularity of the matrices to be inverted),
while the first does not.

@@

If the first method (equation~\ref{eq:T-restr}) is chosen
to impose these restrictions,
the matrix of regressors $X$ is (post-)\hspace{0pt}multiplied
by the $M$ matrix,
so that
\begin{equation}
    X^M = X \cdot M .
\end{equation}
Then, $X^M$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\bHat^M$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the estimated covariance matrix of the original parameters
can be obtained by
\begin{equation}
   \COVHat \left[ \bHat \right]
   = M \cdot \COVHat \left[ \bHat^M \right] \cdot M' .
\end{equation}

>>>>

The first method is less flexible than the second%
\footnote{
While restrictions like $\beta_1 = 2 \beta_2$ can be imposed by
both methods,
restrictions like $\beta_1 + \beta_2 = 4$ can be imposed only
by the second method.
}, 
but is preferable if equality constraints for coefficients
across many equations of the system are imposed. 
Of course, these restrictions can be also imposed using
the latter method.
However, while the latter method increases the dimension of the 
matrices to be inverted during estimation, the first reduces it. 
Thus, in some cases the latter way leads to estimation problems
(e.g.\ (near) singularity of the matrices to be inverted),
while the first does not.

@@

If the first method (equation~\ref{eq:T-restr}) is chosen
to impose these restrictions,
the matrix of regressors $X$ is (post-)\hspace{0pt}multiplied
by the $M$ matrix,
so that
\begin{equation}
    X^M = X \cdot M .
\end{equation}
Then, $X^M$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols-wls-sur}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\bHat^M$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the estimated covariance matrix of the original parameters
can be obtained by
\begin{equation}
   \COVHat \left[ \bHat \right]
   = M \cdot \COVHat \left[ \bHat^M \right] \cdot M' .
\end{equation}
